Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
AR expanded taken

AR_expanded <- my_apriori(transactions_expanded)
# creating vector of fail course
course_id_fail <- d_transactions_expanded %>%
  filter(PF == "fail") %>%
  distinct(`item_PF`)

@@

#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
     AR_expanded, AR_expanded_PF, AR_expanded_HL,
     file = "App/AR.RDATA")

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded, AR_expanded_PF, AR_expanded_HL)

>>>>

AR_expanded_taken <- my_apriori(transactions_expanded)
# creating vector of fail course
course_id_fail <- d_transactions_expanded %>%
  filter(PF == "fail") %>%
  distinct(`item_PF`)

@@

#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL,
     file = "App/AR.RDATA")

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)
